\section{conclusion}
\label{sec:conclusion}
Video communications are power-hungry. Real-time video calls add additional challenges because real-time video calls are highly delay sensitive and no video frames are available in advance. In this paper, we explore the possibility of using backlight scaling technique to save the display power consumption during real-time video calls. For this purpose, we have designed and implemented LCD-GDP. In LCD-GDP, the luminance scanning and generation is migrated to the sender side during video capturing and the information is piggybacked to the receiver. Furthermore, we propose a greedy algorithm that is practical for backlight determination in real-time video calls. Lastly, LCD-GDP leverages the GPU instead of the CPU to conduct real-time luminance compensation. We build LCD-GDP based on the WebRTC and our evaluations on a smartphone and a tablet show that upto 33\% of power consumption can be saved without affecting the video call quality.

%% In this paper, we explored the possibility of applying backlight
%% scaling technique for real-time communication on the mobile devices,
%% and proposed the LCD-GDP to reduce the power consumption during the
%% video calls. We identified the challenges of efficiently migrating the
%% computation intensive tasks from offline to online. In order to scan
%% each frame for generating luminance histogram only once, we located
%% the scanning module at sender side and piggybacked the luminance
%% information in duplicated way. We also used a greedy algorithm to
%% replace the commonly applied dynamic programming technique for keeping
%% the communication latency as low as possible.  Finally, we take
%% advantage of the GPU to compensate the pixel luminance and to make
%% color conversation in a timely manner. We built our LCD-GDP into a
%% WebRTC app on Android platform and then evaluated the
%% performance. From the evaluation, upto $33\%$ power consumption is
%% saved on average by using our LCD-GDP. At the same time, the quality
%% of services in fps and latency stay in the same level as the original
%% real-time streaming. Little distortion in PSNR and SSIM is introduced
%% by activating LCD-GDP.

